Binocular integration of chromatic and luminance signals

### 2024-03-31 manuscript.Rmd
First draft completed

processdata <- 0
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)

@@

# other Stan settings
burnInSteps <- 5000   # Number of steps to "tune" the samplers
thinSteps <- 10
nChains <- 8

@@

if (processdata>1){
  use_miniconda('r-reticulate')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

ticklocs <- seq(-1,1,0.5)
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
title(xlab="L", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

text(-0.95,0.9,'(a)',cex=2)

@@

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
title(xlab="L+M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="S", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

text(-0.95,0.9,'(b)',cex=2)

@@

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0.1, upper=3>[Ndatasets] p;
    vector<lower=2, upper=8>[Ndatasets] q;
    vector<lower=1, upper=2>[Ndatasets] m;
    vector<lower=0.001, upper=2>[Ndatasets] S;  
    vector<lower=0.001, upper=1>[Ndatasets] Z;
    vector<lower=0.001,upper=2>[Ndatasets] w;
    vector<lower=0.001,upper=1>[Ndatasets] k;

    real<lower=0> sigma ;
    real<lower=0.1> pmu ; 
    real<lower=2> qmu ; 
    real<lower=1> mmu ;
    real<lower=0.001> Smu ;
    real<lower=0.001, upper=1> Zmu ; 
    real<lower=0.001> wmu ; 
    real<lower=0.001> kmu ;

@@

    pmu ~ normal( 1.4 , 0.1 ) ;
    qmu ~ normal( 6.59 , 0.5 ) ;
    mmu ~ normal( 1.28 , 0.2 ) ;
    Smu ~ normal( 0.985 , 0.2 ) ;
    Zmu ~ normal( 0.1 , 0.5 ) ;
    wmu ~ normal( 1 , 0.2 ) ;
    kmu ~ normal( 0.194 , 0.1 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

@@

allstanparams <- matrix(0,nrow=4,ncol=7)

@@

  allsamples[expt,1,] <- plist
  allsamples[expt,2,] <- qlist
  allsamples[expt,3,] <- mlist
  allsamples[expt,4,] <- Slist
  allsamples[expt,5,] <- Zlist
  allsamples[expt,6,] <- wlist
  allsamples[expt,7,] <- klist
}

@@

nrandomdraws <- 200

@@

  paramorder <- c('p','q','m','w','S','Z','k')
  paramvalorder <- c(1,2,3,6,4,5,7)

  xstart <- c(1,1,1/2,1/2,1/4,1/32,1/16)
  xstartdB <- round(20*log10(xstart))
  xstep <- c(6,6,3,3,6,12,6)

@@

    ticklabelsx <- c('1/4','1/2',1,2,4)
    if (param<3){ticklabelsx <- c(1,2,4,8,16)}
    if (param==3 || param==4){ticklabelsx <- c('1/2','','1','','2')}
    if (param>5){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
    if (param==6){ticklabelsx <- c('1/32','1/8','1/2','2','8')}

@@

paneltitles <- c('Achromatic grating','Red/green grating','Blue/yellow grating','Flickering disc')

  for (expt in 1:4){
  pedlist <- -12:36
  pedlevelsC <- 10^(pedlist/20)
  pedlevelsC[1] <- 0
  allpred <- array(0,dim=c(4,length(pedlist)))
  allrandomdips <- array(0,dim=c(nrandomdraws,4,length(pedlist)))
  drawindices <- sample(dim(allsamples)[3],nrandomdraws,replace=FALSE)
  for (cond in 1:4){
    for (pedlev in 1:length(pedlist)){
      allpred[cond,pedlev] <- discriminate(allstanparams[expt,],pedlevelsC[pedlev],cond)

      for (n in 1:nrandomdraws){
        allrandomdips[n,cond,pedlev] <- discriminate(allsamples[expt,,drawindices[n]],pedlevelsC[pedlev],cond)
      }
    }
  }
  allrandomdips <- 20*log10(allrandomdips)

@@

  allpreddB <- 20*log10(allpred)

@@

    for (n in 1:nrandomdraws){
      lines(pedlist,allrandomdips[n,cond,],col=addalpha(collist[cond],2/nrandomdraws),lwd=2)
    }

    lines(pedlist,allpreddB[cond,],col=collist[cond],lwd=2)
    # points(pedcontrasts,threshtoplot[expt,cond,],pch=16,col=collist[cond],cex=1.5)
  }
  text(-9,33,paste0('(',letters[expt],')'),cex=2)
  # legend(-12,42,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
  }

@@

  dev.off()
}

@@

>>>>

processdata <- 1
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)

@@

# other Stan settings
burnInSteps <- 5000   # Number of steps to "tune" the samplers
thinSteps <- 10
nChains <- 64

@@

if (processdata>0){
  use_miniconda('r-reticulate')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

@@

ticklocs <- seq(-1,1,0.5)
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
title(xlab="L", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(a) L-M gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)

@@

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,1), ylim=c(-1,1))  
axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     
axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
mtext(text = ticklocs, side = 1, at=ticklocs, line=0.3)    
mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
title(xlab="L+M", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="S", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) S-(L+M) gratings', col.lab=rgb(0,0,0), line=1.5, cex.lab=2)

@@

```{r stanmodelspecifications, include=FALSE}

modelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0.1, upper=3>[Ndatasets] p;
    vector<lower=2, upper=8>[Ndatasets] q;
    vector<lower=0.5, upper=2>[Ndatasets] m;
    vector<lower=0.001, upper=2>[Ndatasets] S;  
    vector<lower=0.001, upper=2>[Ndatasets] Z;
    vector<lower=0.001, upper=2>[Ndatasets] w;
    vector<lower=0.001, upper=2>[Ndatasets] k;

    real<lower=0> sigma ;
    real<lower=0.1, upper=3> pmu ; 
    real<lower=2, upper=8> qmu ; 
    real<lower=0.5, upper=2> mmu ;
    real<lower=0.001, upper=2> Smu ;
    real<lower=0.001, upper=2> Zmu ; 
    real<lower=0.001, upper=2> wmu ; 
    real<lower=0.001, upper=2> kmu ;

@@

    pmu ~ normal( 1.4 , 0.1 ) ;
    qmu ~ normal( 6.59 , 0.5 ) ;
    mmu ~ normal( 1.28 , 0.2 ) ;
    Smu ~ normal( 0.985 , 0.2 ) ;
    Zmu ~ normal( 0.08 , 0.5 ) ;
    wmu ~ normal( 1 , 0.2 ) ;
    kmu ~ normal( 0.194 , 0.1 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    psigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    qsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    msigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Ssigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

@@

crossmodelString = "
  data {
    int<lower=1> Ndatasets ;
    int<lower=1> Ntotal ;
    int ncorrect[Ntotal] ;
    int ntrials[Ntotal] ;
    real PedestalContrast[Ntotal] ;
    real TargetContrast[Ntotal] ;
    int<lower=1> c[Ntotal] ;
    int<lower=1> s[Ntotal] ;  
  }
  parameters {
    vector<lower=0, upper=40>[Ndatasets] Zac;
    vector<lower=0, upper=40>[Ndatasets] Zrg;
    vector<lower=0, upper=40>[Ndatasets] Zby;
    vector<lower=0.001, upper=2>[Ndatasets] wAcR;
    vector<lower=0.001, upper=2>[Ndatasets] wAcB;
    vector<lower=0.001, upper=2>[Ndatasets] wRgA;
    vector<lower=0.001, upper=2>[Ndatasets] wRgB;
    vector<lower=0.001, upper=2>[Ndatasets] wByA;
    vector<lower=0.001, upper=2>[Ndatasets] wByR;

    real<lower=0> sigma ;
    real<lower=0, upper=40> Zacmu ; 
    real<lower=0, upper=40> Zrgmu ; 
    real<lower=0, upper=40> Zbymu ; 
    real<lower=0.001, upper=2> wAcRmu ; 
    real<lower=0.001, upper=2> wAcBmu ; 
    real<lower=0.001, upper=2> wRgAmu ; 
    real<lower=0.001, upper=2> wRgBmu ; 
    real<lower=0.001, upper=2> wByAmu ; 
    real<lower=0.001, upper=2> wByRmu ;

    real<lower=0> Zacsigma ;    
    real<lower=0> Zrgsigma ;    
    real<lower=0> Zbysigma ;    
    real<lower=0> wAcRsigma ;
    real<lower=0> wAcBsigma ;
    real<lower=0> wRgAsigma ;
    real<lower=0> wRgBsigma ;
    real<lower=0> wByAsigma ;
    real<lower=0> wByRsigma ;
  }
  model {
    Zacmu ~ normal( 10 , 5 ) ;
    Zrgmu ~ normal( 10 , 5 ) ;
    Zbymu ~ normal( 10 , 5 ) ;
    wAcRmu ~ normal( 0.5 , 0.3 ) ;
    wAcBmu ~ normal( 0.5 , 0.3 ) ;
    wRgAmu ~ normal( 0.5 , 0.3 ) ;
    wRgBmu ~ normal( 0.5 , 0.3 ) ;
    wByAmu ~ normal( 0.5 , 0.3 ) ;
    wByRmu ~ normal( 0.5 , 0.3 ) ;
    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    Zacsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    Zrgsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    Zbysigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;    
    wAcRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wAcBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wRgAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wRgBsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wByAsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
    wByRsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;

    Zac ~ normal( Zacmu , Zacsigma ) ; // vectorized
    Zrg ~ normal( Zrgmu , Zrgsigma ) ; // vectorized
    Zby ~ normal( Zbymu , Zbysigma ) ; // vectorized
    wAcR ~ normal( wAcRmu , wAcRsigma ) ; // vectorized
    wAcB ~ normal( wAcBmu , wAcBsigma ) ; // vectorized
    wRgA ~ normal( wRgAmu , wRgAsigma ) ; // vectorized
    wRgB ~ normal( wRgBmu , wRgBsigma ) ; // vectorized
    wByA ~ normal( wByAmu , wByAsigma ) ; // vectorized
    wByR ~ normal( wByRmu , wByRsigma ) ; // vectorized

    if (c[i]==1) { // achromatic detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==2) { // red/green detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==3) { // blue/yellow detection condition
    Lt = pow(TargetContrast[i],1.21) / (1.03 + (TargetContrast[i])) ;
    Rt = 0 ;
    Ln = 0 ;
    Rn = 0 ;

    targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
    nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==4) { // achromatic target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==5) { // red/green target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgA[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==6) { // blue/yellow target, achromatic mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByA[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==7) { // achromatic target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcR[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==8) { // red/green target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
      Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==9) { // blue/yellow target, red/green mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wByR[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

     if (c[i]==10) { // achromatic target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wAcB[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zac[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zac[s[i]] + pow((Ln + Rn), 6.4)) ;

    if (c[i]==11) { // red/green target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + wRgB[s[i]]*PedestalContrast[i]) ;
      Rt = 0 ;
      Ln = 0 ;
      Rn = 0 ;

      targresp = pow((Lt + Rt), 7.82) / (Zrg[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zrg[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    if (c[i]==12) { // blue/yellow target, blue/yellow mask
      Lt = pow(TargetContrast[i],1.21) / (1.03 + TargetContrast[i] + 1*PedestalContrast[i]) ;
     Rt = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i] + 1*TargetContrast[i]) ;
      Ln = 0 ;
      Rn = pow(PedestalContrast[i],1.21) / (1.03 + PedestalContrast[i]) ;

      targresp = pow((Lt + Rt), 7.82) / (Zby[s[i]] + pow((Lt + Rt), 6.4)) ;
      nullresp = pow((Ln + Rn), 7.82) / (Zby[s[i]] + pow((Ln + Rn), 6.4)) ;     
    }

    dprime = (targresp-nullresp)/0.23 ;
    if (is_nan(dprime)){
       dprime = 0;
    }
    if (is_inf(dprime)){
       dprime = 10;
    }
    if (dprime > 10){
       dprime = 10;
    }    
    ncorrect[i] ~ binomial(ntrials[i], Phi(dprime/sqrt(2))) ;
    }
  }  
" # close quote for modelString

@@

allstanparams <- matrix(0,nrow=4,ncol=7)
upperstanparams <- matrix(0,nrow=4,ncol=7)
lowerstanparams <- matrix(0,nrow=4,ncol=7)

@@

  allsamples[expt,1,] <- plist
  allsamples[expt,2,] <- qlist
  allsamples[expt,3,] <- mlist
  allsamples[expt,4,] <- Slist
  allsamples[expt,5,] <- Zlist
  allsamples[expt,6,] <- wlist
  allsamples[expt,7,] <- klist

  # quants <- quantile(wlist,probs=c(0.025,0.975))
  # i <- which.min(abs(wlist-quants[1]))
  # lowerstanparams[expt,] <- allsamples[expt,,i]
  # i <- which.min(abs(wlist-quants[2]))
  # upperstanparams[expt,] <- allsamples[expt,,i]
}

@@

@@

  paramorder <- c('p','q','m',expression(omega),'S','Z','k')
  paramvalorder <- c(1,2,3,6,4,5,7)

  xstart <- c(1,1,1/2,1/2,1/4,1/64,1/16)
  xstartdB <- round(20*log10(xstart))
  xstep <- c(6,6,3,3,6,12,6)

@@

    ticklabelsx <- c('1/4','1/2',1,2,4)
    if (param<3){ticklabelsx <- c(1,2,4,8,16)}
    if (param==3 || param==4){ticklabelsx <- c('1/2','','1','','2')}
    if (param>5){ticklabelsx <- c('1/16','1/8','1/4','1/2','1')}
    if (param==6){ticklabelsx <- c('1/64','1/16','1/4','1','4')}

@@

paneltitles <- c('(a) Achromatic grating','(b) Red/green grating','(c) Blue/yellow grating','(d) Flickering disc')

  for (expt in 1:4){
    print(expt)
  pedlist <- -12:36
  pedlevelsC <- 10^(pedlist/20)
  pedlevelsC[1] <- 0
  allpred <- array(0,dim=c(4,length(pedlist)))
  # upperpred <- array(0,dim=c(4,length(pedlist)))
  # lowerpred <- array(0,dim=c(4,length(pedlist)))
  for (cond in 1:4){
    for (pedlev in 1:length(pedlist)){
      allpred[cond,pedlev] <- discriminate(allstanparams[expt,],pedlevelsC[pedlev],cond)
      # upperpred[cond,pedlev] <- discriminate(upperstanparams[expt,],pedlevelsC[pedlev],cond)
      # lowerpred[cond,pedlev] <- discriminate(lowerstanparams[expt,],pedlevelsC[pedlev],cond)
    }
  }

@@

  allpreddB <- 20*log10(allpred)
  # lowerpreddB <- 20*log10(lowerpred)
  # upperpreddB <- 20*log10(upperpred)

@@

    # polygon(pedlist[c(1:length(pedlist),length(pedlist):1)],c(lowerpreddB[cond,],upperpreddB[cond,length(pedlist):1]),border=NA,col=addalpha(collist[cond],alpha=0.2))
    lines(pedlist,allpreddB[cond,],col=collist[cond],lwd=2)
    # points(pedcontrasts,threshtoplot[expt,cond,],pch=16,col=collist[cond],cex=1.5)
  }
  # text(-9,33,paste0('(',letters[expt],')'),cex=2)
  # legend(-12,42,c('Monocular','Binocular','Half-binocular','Dichoptic'),pch=16,col=collist,box.lwd=2,cex=1.5)
  }

@@

@@

```{r domodellingMCS, include=FALSE}

# Translate to C++ and compile to DSO:
mcsmodel <- stan_model(model_code=crossmodelString)

ex2data <- read.csv('local/Experiment2.csv')

sublist <- unique(ex2data$Subject)
targetlist <- unique(ex2data$TargetType)
pedlist <- unique(ex2data$PedestalType)
pedlist <- pedlist[c(4,1,3,2)]  # reorder to make life easier later

counter <- 0
datasetcounter <- 0
ntrials <- NULL
ncorrect <- NULL
subjects <- NULL
datasets <- NULL
conditions <- NULL
pedestals <- NULL
targets <- NULL

for (s in 1:3){
    datasetcounter <- datasetcounter + 1
    conditioncounter <- 0
    for (pedtype in 1:4){
    for (targtype in 1:3){
      conditioncounter <- conditioncounter + 1
      thiscond <- subset(ex2data,Subject==sublist[s] & TargetType==targetlist[targtype] & PedestalType==pedlist[pedtype])

        pedcont <- sort(unique(thiscond$PedestalContrast))
        targconts <- sort(unique(thiscond$TargetContrast))

        for (t in 1:length(targconts)){
          counter <- counter + 1
          thislevel <- subset(thiscond,TargetContrast==targconts[t])
          ntrials[counter] <- nrow(thislevel)
          ncorrect[counter] <- sum(thislevel$IsCorrect)
          subjects[counter] <- s
          datasets[counter] <- datasetcounter
          conditions[counter] <- conditioncounter
          pedestals[counter] <- pedcont
          targets[counter] <- targconts[t]

      }
    }
  }
}

thisexpt <- data.frame(datasets,subjects,conditions,pedestals,targets,ntrials,ncorrect)

# Get MC sample of posterior:
stanFit <- sampling(object=mcsmodel, 
                    data = dataList, 
                    chains = nChains,
                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
                    warmup = burnInSteps, 
                    thin = thinSteps,
                    cores = getOption("mc.cores", 1L))

save(file=paste0('local/MCSfit.RData'),list=c('stanFit'))

```{r plotMCSstan, include=FALSE}

getmodelresp3inputs <- function(p,La,Ra,Lr,Rr,Lb,Rb){

  maxlength <- max(length(La),length(Ra),length(Lr),length(Rr),length(Lb),length(Rb))
  resp <- matrix(0,nrow=3,ncol=maxlength)

  LrespA <- (La^1.21)/(1.03 + La + Ra + p[4]*Rr + p[5]*Rb)
  RrespA <- (Ra^1.21)/(1.03 + Ra + La + p[4]*Lr + p[5]*Lb)
  LrespR <- (Lr^1.21)/(1.03 + Lr + p[6]*Ra + Rr + p[7]*Rb)
  RrespR <- (Rr^1.21)/(1.03 + Rr + p[6]*La + Lr + p[7]*Lb)
  LrespB <- (Lb^1.21)/(1.03 + Lb + p[8]*Ra + p[9]*Rr + Rb)
  RrespB <- (Rb^1.21)/(1.03 + Rb + p[8]*La + p[9]*Lr + Lb)

  bs <- LrespA + RrespA
  resp[1,] <- (bs^7.82)/(p[1] + bs^6.4)

  bs <- LrespR + RrespR
  resp[2,] <- (bs^7.82)/(p[2] + bs^6.4)

  bs <- LrespB + RrespB
  resp[3,] <- (bs^7.82)/(p[3] + bs^6.4)

return(resp)}

predictpmfs <- function(p){

  contrastsC <- 10^(targetcontsdB/20)
  pmfout <- matrix(0,nrow=12,ncol=length(contrastsC))

  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,0)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
  dprime <- (tr[1,] - nr[1,])/0.23
  pmfout[1,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,0)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
  dprime <- (tr[2,] - nr[2,])/0.23
  pmfout[2,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,0)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,0)
  dprime <- (tr[3,] - nr[3,])/0.23
  pmfout[3,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,contrastsC,16,0,0,0,0)
  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
  dprime <- (tr[1,] - nr[1,])/0.23
  pmfout[4,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,16,contrastsC,0,0,0)
  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
  dprime <- (tr[2,] - nr[2,])/0.23
  pmfout[5,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,16,0,0,contrastsC,0)
  nr <- getmodelresp3inputs(p,0,16,0,0,0,0)
  dprime <- (tr[3,] - nr[3,])/0.23
  pmfout[6,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,contrastsC,0,0,64,0,0)
  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
  dprime <- (tr[1,] - nr[1,])/0.23
  pmfout[7,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,contrastsC,64,0,0)
  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
  dprime <- (tr[2,] - nr[2,])/0.23
  pmfout[8,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,0,64,contrastsC,0)
  nr <- getmodelresp3inputs(p,0,0,0,64,0,0)
  dprime <- (tr[3,] - nr[3,])/0.23
  pmfout[9,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,contrastsC,0,0,0,0,64)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
  dprime <- (tr[1,] - nr[1,])/0.23
  pmfout[10,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,contrastsC,0,0,64)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
  dprime <- (tr[2,] - nr[2,])/0.23
  pmfout[11,] <- 100*pnorm(dprime/sqrt(2))

  tr <- getmodelresp3inputs(p,0,0,0,0,contrastsC,64)
  nr <- getmodelresp3inputs(p,0,0,0,0,0,64)
  dprime <- (tr[3,] - nr[3,])/0.23
  pmfout[12,] <- 100*pnorm(dprime/sqrt(2))

return(pmfout)}

load('local/MCSfit.RData')
draws <- extract(stanFit)
Zac <- mean(draws$Zacmu)
Zrg <- mean(draws$Zrgmu)
Zby <- mean(draws$Zbymu)
wAcR <- mean(draws$wAcRmu)
wAcB <- mean(draws$wAcBmu)
wRgA <- mean(draws$wRgAmu)
wRgB <- mean(draws$wRgBmu)
wByA <- mean(draws$wByAmu)
wByR <- mean(draws$wByRmu)

Zaclist <- draws$Zacmu
Zrglist <- draws$Zrgmu
Zbylist <- draws$Zbymu
wAcRlist <- draws$wAcRmu
wAcBlist <- draws$wAcBmu
wRgAlist <- draws$wRgAmu
wRgBlist <- draws$wRgBmu
wByAlist <- draws$wByAmu
wByRlist <- draws$wByRmu

targetcontsdB <<- seq(-12,42,1)
allpmfpreds <- predictpmfs(c(Zac,Zrg,Zby,wAcR,wAcB,wRgA,wRgB,wByA,wByR))

titlelist <- c('(a) Achromatic target','(b) R/G target','(c) B/Y target')

    pdf(paste0('Figures/MCSmodel.pdf'),width=12,height=8)

    par(mfrow=c(2,3))
    # layout(matrix(c(1,1,2,2,3,3,0,4,4,5,5,0),2,6,byrow=TRUE))

  lines(targetcontsdB,allpmfpreds[cond,],lwd=3)
  # lines(targetcontsdB,allmodelpreds[cond,],lwd=3)
  # points(contrastsdB[cond,],propcorr[cond,],pch=21,lwd=3,cex=2,bg='black')
